	\documentclass[a4paper,12pt]{book}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{lipsum}
%\usepackage[utf8]{inputenc}
%\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{tcolorbox}
\usepackage{color}   %May be necessary if you want to color links
\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\DeclareSymbolFontAlphabet{\mathnormal}{letters}
\begin{document}

\title{Notes on  Tensors}
\author{Pugazharasu A D \\
	Email: \href{mailto:pugazhin202@gmail.com}{pugazhin202@gmail.com}\footnote{Department of Physics, Loyola College, Chennai}}


\frontmatter
\maketitle 
\nopagebreak
\tableofcontents

\mainmatter

%\chapter*{Preface}
%The following is a set of review notes I made for . It asssumes the following,
%\begin{itemize}
%	\item Linear Algebra
%	\item Multivariable and Vector Calculus/Vector Analysis
%\end{itemize}
%If you wish to brush up on those topics you can head to my notes on them by clicking on the links. These are not notes for study but rather for review, thus I assume you have at least skimmed through some material on Tensors and simply wish to either refresh or double check things. The references I used to create this can be found here. A \\
% I'd like to acknowledge the support of Prof. Joseph Prabagar and from Loyola College, my partner in crime Rishi Kumar and everyone who have read this document to. 
\include{./Chapters/Tensor-Algebra}
\include{./Chapters/Tensor-Calculus}
\backmatter
\begin{thebibliography}{9}
	\bibitem{p1} Fleisch, D. A. (2018). A student's guide to vectors and tensors. Cambridge: Cambridge University Press
	
	\bibitem {p2} Jeevanjee, N. (2015). An introduction to tensors and group theory for physicists: Nadir Jeevanjee. Cham: Birkhauser.
	
	\bibitem {p3} Kees Dullemond \& Kasper Peeters (1991), Introduction to Tensor Calculus 
	
	\bibitem {p4} Nakahara, M. (2017). Geometry, Topology and Physics. Boca Raton, FL: CRC Press.
	
	\bibitem {p5} Arfken, G., Weber, H. J., \& Harris, F. E. (2013). Mathematical methods for physicists. Amsterdam: Elsevier Academic Press.
	
	\bibitem {p6} Riley, K. F., \& Hobson, M. P. (2008). Mathematical methods for physics and engineering a comprehensive guide. Cambridge: Cambridge University Press.
	
	\bibitem {p7} Carroll, S. M. (2019). Spacetime and geometry an introduction to general relativity. Cambridge: Cambridge University Press.
	
	\bibitem {p8} Das, A. J. (2007). Tensors: The Mathematics of Relativity Theory and Continuum Mechanics. New York: Springer Science Business Media, LLC
	
	\bibitem {p9} Millman, R. S., \&; Parker, G. D. (1984). Elements of differential geometry. Taipei: Tan Chiang.
	
	\bibitem {p10} Faber, R. L. (1983). Differential geometry and relativity theory. New York: Marcel Dekker.	
\end{thebibliography}
% bibliography, glossary and index would go here.

\end{document}